### 2019-09-20 reports/thesis/book.tex
Revise

\begin{titlingpage}
\centering
{\LARGE Characterisation of Computed Tomography Noise in Projection Space with Applications to Additive Manufacturing \par}
\vspace{1cm}
{\Large Sherman E.~Lo\par}
{\Large Doctor of Philosophy in Statistics\par}
\vfill
\includegraphics[width = 0.75\textwidth]{../figures/frontCover.jpg}
\vfill
{\Large University of Warwick\par}
{\Large Department of Statistics\par}
{\Large September 2019\par}
\end{titlingpage}

@@

This work is funded by the EPSRC and MRC Centre for Doctoral Training in Next Generation Statistical Science: The Oxford-Warwick Statistics Programme (EP/L016710/1). I would like to thank my cohort for the friendship and collaboration during the programme: Nathan Cunningham, Giuseppe di Benedetto, Beniamino Hadj-Amar, Jack Jewson, Ella Kaye, Leon Law, Kaspar M\"{a}rtens, Marcin Mider, Xenia Miscouridou, Paul Vanetti and Andi Wang.

>>>>

\begin{titlingpage}
\centering
{\LARGE Characterisation of Computed Tomography Noise in Projection Space with Applications to Additive Manufacturing \par}
\vspace{1cm}
{\Large Sherman Edea Lo\par}
{\Large Doctor of Philosophy in Statistics\par}
\vfill
\includegraphics[width = 0.75\textwidth]{../figures/frontCover.jpg}
\vfill
{\Large University of Warwick\par}
{\Large Department of Statistics\par}
{\Large September 2019\par}
\end{titlingpage}

@@

This work is funded by the EPSRC and MRC Centre for Doctoral Training in Next Generation Statistical Science: The Oxford-Warwick Statistics Programme (EP/L016710/1). I would like to thank my cohort for the friendship and collaboration during the programme: Nathan Cunningham, Giuseppe di Benedetto, Beniamino Hadj-Amar, Jack Jewson, Ella Kaye, Leon Law, Kaspar M\"{a}rtens, Marcin Mider, Xenia Miscouridou, Paul Vanetti, Andi Wang.

### 2019-09-20 reports/thesis/chapters/1_literatureReview.tex
Typo
Revise

There are various discontinuities in AM. In FDM, a staircase effect on the surface of the product arises from poor slicing methods of the CAD model \citep{weeren1995quality}. Internal voids can be formed due to insufficient material flow \citep{weeren1995quality}. Other factors which can cause defects include misalignment of the platform or nozzle, depletion of material and lack of adhesion due to low temperatures \citep{gunaydin2018common}.

@@

An algorithm was developed to adjust the parameters of the simulation as well as aligning it so that it fits with the x-ray acquisition \citep{brierley2018optimized}. However, it is very complicated as it is optimising over a very large dimensional space \citep{brierley2018optimized}. It was demonstrated that detection of defects is possible in projection space by comparing two simulated projections with each other, one with defects and the other without \citep{brierley2018optimized}. Another method is to use machine learning methods to classify defects from a projection \citep{rale2009comparison}.

>>>>

There are various discontinuities in AM. In fused deposition modelling, a staircase effect on the surface of the product arises from poor slicing methods of the CAD model \citep{weeren1995quality}. Internal voids can be formed due to insufficient material flow \citep{weeren1995quality}. Other factors which can cause defects include misalignment of the platform or nozzle, depletion of material and lack of adhesion due to low temperatures \citep{gunaydin2018common}.

@@

An algorithm was developed to adjust the parameters of the simulation as well as aligning it so that it fits with the x-ray acquisition \citep{brierley2018optimized}. However, it is very complicated as it is optimising over a very large dimensional space \citep{brierley2018optimized}. Studies have been conducted comparing simulated projections with each other, one with defects and the other without, by looking at the contrast to noise ratio of the defects. This is done at various projection angles as part of a large optimisation problem \citep{brierley2018optimized}. Another method is to use machine learning methods to classify defects from a projection \citep{rale2009comparison}.

### 2019-09-20 reports/thesis/chapters/2_dataCollection.tex
Revise

\begin{figure}[p]
  \centering
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/AbsNoFilterDeg30.eps}
      \caption{Obtained projection at \SI{36}{\watt}}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/AbsNoFilterDeg30_sim.eps}
      \caption{Simulated projection at \SI{36}{\watt}}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/AbsNoFilter_calibration1.eps}
      \caption{Greyscale projection at \SI{0}{\watt}}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/AbsNoFilter_calibration5.eps}
      \caption{Greyscale projection at \SI{36}{\watt}}
    \end{subfigure}
  }
  \caption{\texttt{AbsNoFilter} projections at \ang{30}; note the colour scale may vary.}
  \label{fig:data_AbsNoFilter}
\end{figure}

\begin{figure}[p]
  \centering
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/AbsFilterDeg30.eps}
      \caption{Obtained projection at \SI{20}{\watt}}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/AbsFilterDeg30_sim.eps}
      \caption{Simulated projection at \SI{20}{\watt}}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/AbsFilter_calibration1.eps}
      \caption{Greyscale projection at \SI{0}{\watt}}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/AbsFilter_calibration5.eps}
      \caption{Greyscale projection at \SI{20}{\watt}}
    \end{subfigure}
  }
  \caption{\texttt{AbsFilter} projections at \ang{30}; note the colour scale may vary.}
  \label{fig:data_AbsFilter}
\end{figure}

\begin{figure}[p]
  \centering
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/TiFilterDeg30.eps}
      \caption{Obtained projection at \SI{20}{\watt}}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/TiFilterDeg30_sim.eps}
      \caption{Simulated projection at \SI{20}{\watt}}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/TiFilter_calibration1.eps}
      \caption{Greyscale projection at \SI{0}{\watt}}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/TiFilter_calibration3.eps}
      \caption{Greyscale projection at \SI{20}{\watt}}
    \end{subfigure}
  }
  \caption{\texttt{TiFilter} projections at \ang{30}; note the colour scale may vary.}
  \label{fig:data_TiFilter}
\end{figure}

@@

\begin{figure}
  \centering
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_image_null.eps}
      \caption{No shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_image_linear.eps}
      \caption{Linear shading correction}
    \end{subfigure}
  }
  \caption{Projection of \texttt{AbsNoFilter} at \ang{30} with and without shading correction.}
  \label{fig:data_shadingCorrectionExample_image}
\end{figure}

@@

\begin{figure}
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_black_null.eps}
      \caption{Black - No shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_white_null.eps}
      \caption{White - No shading correction}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_black_bw.eps}
      \caption{Black - BW shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_white_bw.eps}
      \caption{White - BW shading correction}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_black_linear.eps}
      \caption{Black - Linear shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_white_linear.eps}
      \caption{White - Linear shading correction}
    \end{subfigure}
  }
  \caption{The black and white images before and after shading correction from the \texttt{AbsNoFilter} dataset.}
  \label{fig:data_shadingCorrectionExample_greyscale}
\end{figure}

>>>>

\begin{figure}[p]
  \centering
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/AbsNoFilterDeg30.eps}
      \caption{Obtained projection at \SI{36}{\watt}}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/AbsNoFilterDeg30_sim.eps}
      \caption{Simulated projection at \SI{36}{\watt}}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/AbsNoFilter_calibration1.eps}
      \caption{Greyscale projection at \SI{0}{\watt}}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/AbsNoFilter_calibration5.eps}
      \caption{Greyscale projection at \SI{36}{\watt}}
    \end{subfigure}
  }
  \caption{\texttt{AbsNoFilter} projections at \ang{30}. The colour scales are in units of \SI{}{\adu}.}
  \label{fig:data_AbsNoFilter}
\end{figure}

\begin{figure}[p]
  \centering
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/AbsFilterDeg30.eps}
      \caption{Obtained projection at \SI{20}{\watt}}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/AbsFilterDeg30_sim.eps}
      \caption{Simulated projection at \SI{20}{\watt}}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/AbsFilter_calibration1.eps}
      \caption{Greyscale projection at \SI{0}{\watt}}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/AbsFilter_calibration5.eps}
      \caption{Greyscale projection at \SI{20}{\watt}}
    \end{subfigure}
  }
  \caption{\texttt{AbsFilter} projections at \ang{30}. The colour scales are in units of \SI{}{\adu}.}
  \label{fig:data_AbsFilter}
\end{figure}

\begin{figure}[p]
  \centering
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/TiFilterDeg30.eps}
      \caption{Obtained projection at \SI{20}{\watt}}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/TiFilterDeg30_sim.eps}
      \caption{Simulated projection at \SI{20}{\watt}}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/TiFilter_calibration1.eps}
      \caption{Greyscale projection at \SI{0}{\watt}}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/TiFilter_calibration3.eps}
      \caption{Greyscale projection at \SI{20}{\watt}}
    \end{subfigure}
  }
  \caption{\texttt{TiFilter} projections at \ang{30}. The colour scales are in units of \SI{}{\adu}.}
  \label{fig:data_TiFilter}
\end{figure}

@@

\begin{figure}
  \centering
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_image_null.eps}
      \caption{No shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_image_linear.eps}
      \caption{Linear shading correction}
    \end{subfigure}
  }
  \caption{Projection of \texttt{AbsNoFilter} at \ang{30} with and without shading correction. The colour scales are in units of \SI{}{\adu}.}
  \label{fig:data_shadingCorrectionExample_image}
\end{figure}

@@

\begin{figure}
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_black_null.eps}
      \caption{Black - No shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_white_null.eps}
      \caption{White - No shading correction}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_black_bw.eps}
      \caption{Black - BW shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_white_bw.eps}
      \caption{White - BW shading correction}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_black_linear.eps}
      \caption{Black - Linear shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/shadingCorrectionExample_white_linear.eps}
      \caption{White - Linear shading correction}
    \end{subfigure}
  }
  \caption{The black and white images before and after shading correction from the \texttt{AbsNoFilter} dataset. The colour scales are in units of \SI{}{\adu}.}
  \label{fig:data_shadingCorrectionExample_greyscale}
\end{figure}
